\sout{Machine Learning for Global Conquest} \\ Multimatrices and Their Derivatives

### 2020-08-24 Math/book.tex
Making some math notes.

\documentclass[12pt]{book}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathtools}
% Use pdflscape for pdf viewers
\usepackage{pdflscape}
% Use lscape for printing as a book
%\usepackage{lscape}
\usepackage{etoolbox}
\usepackage{csquotes}
\usepackage[normalem]{ulem}
\usepackage[toc,page]{appendix}
% package used for \llparenthesis
\usepackage{stmaryrd}

@@

\DeclareMathOperator{\Dim}{Dim}
\DeclareMathOperator{\Ident}{I}
\DeclareMathOperator{\Tran}{Tran}
\DeclareMathOperator{\Part}{Part}
\DeclareMathOperator{\SoS}{\mathbb{S}}
\DeclareMathOperator{\Softmax}{Softmax}
\DeclareMathOperator{\Sum}{\Sigma}
\DeclareMathOperator{\remainder}{mod}
\DeclareMathOperator{\RMult}{RMult}
\DeclareMathOperator{\LMult}{LMult}
\DeclareMathOperator{\Idx}{Idx}
\DeclareMathOperator{\size}{size}
%\newcommand{\mmult}[1]{\stackrel{\times}{#1}}
%\newcommand{\mmult}[1]{\underset{#1}{\times}}
\newcommand{\mmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\times}$}}}
\newcommand{\dmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\,\bullet\,}$}}}
\newcommand{\mconcat}[1]{\text{\raisebox{1ex}{$\underset{#1}{\oplus}$}}}
\newcommand{\shape}[1]{\left|#1\right|}

@@

>>>>

\documentclass[12pt]{book}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathtools}
% Use pdflscape for pdf viewers
\usepackage{pdflscape}
% Use lscape for printing as a book
%\usepackage{lscape}
\usepackage{etoolbox}
\usepackage{csquotes}
\usepackage[normalem]{ulem}
\usepackage[toc,page]{appendix}
% package used for \llparenthesis
\usepackage{stmaryrd}
\usepackage{hyperref}

@@

\DeclareMathOperator{\Dim}{Dim}
\DeclareMathOperator{\Ident}{I}
\DeclareMathOperator{\Tran}{Tran}
\DeclareMathOperator{\Part}{Part}
\DeclareMathOperator{\SoS}{\mathbb{S}}
\DeclareMathOperator{\Softmax}{Softmax}
\DeclareMathOperator{\Sum}{\Sigma}
\DeclareMathOperator{\remainder}{mod}
\DeclareMathOperator{\RMult}{RMult}
\DeclareMathOperator{\LMult}{LMult}
\DeclareMathOperator{\Idx}{Idx}
\DeclareMathOperator{\size}{size}
\DeclareMathOperator{\FFT}{FFT}
\DeclareMathOperator{\IFFT}{IFFT}
%\newcommand{\mmult}[1]{\stackrel{\times}{#1}}
%\newcommand{\mmult}[1]{\underset{#1}{\times}}
\newcommand{\mmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\times}$}}}
\newcommand{\dmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\,\bullet\,}$}}}
\newcommand{\mconcat}[1]{\text{\raisebox{1ex}{$\underset{#1}{\oplus}$}}}
\newcommand{\shape}[1]{\left|#1\right|}

@@

\chapter{Audio Project}

\begin{landscape}
\section{2d Derivatives with Fast Fourier Transforms}

According to wikipedia \cite{wiki:fourier}, if $f(x)$ is an absolutely continuous differentiable function, and both $f$ and its derivative $f'$ are integrable. Then the Fourier transform of the derivative is given by
\[ \hat{f'}(\xi) = 2 \pi i \xi \hat{f}(\xi) \]

What that means in practice is that we can approximate the derivative of a sequence, or in our case a multimatrix, using a FFT.
The method I'm using comes from a youtube series by Steve Brunton \cite{youtube:fourier} which I've found to be particularly helpful.

We'll define a function, $\FFT(X) = F$, and it's inverse, $\IFFT(F) = X$ as the fast fourier transform of $X$ and it's inverse of $F$.
Specifically, we'll let $X$ be a multimatrix of shape $\shape{X} = \left<N\right>$ where $N = 2^p$ for some $p>1$.
And we'll let $F$ be a multimatrix representing a similar shape of complex numbers, $\shape{F} = \left<N, 2\right>$ where $F[k,1]$ is
the real componenet and $F[k,2]$ is the imaginary component. So,

\[ \FFT(X)[k,1] = \sum_{n=1}^{N} X[n] \cos\left(\frac{2 \pi (k-1)(n-1)}{N}\right) \]
\[ \FFT(X)[k,2] = -\sum_{n=1}^{N} X[n] \sin\left(\frac{2 \pi (k-1)(n-1)}{N}\right) \]
\begin{align*}
  \IFFT(F)[n]
  &= \frac{1}{N} \sum_{k=1}^{N} Real\left( (F[k,1]+i F[k,2]) e^{\frac{2 \pi i (k-1)(n-1)}{N} } \right) \\
  &= \frac{1}{N} \sum_{k=1}^{N} F[k,1] \cos\left(\frac{2 \pi (k-1)(n-1)}{N}\right) - F[k,2] \sin\left(\frac{2 \pi (k-1)(n-1)}{N}\right)
\end{align*}

Now if $X[n] = g(n)$ we can compute $X'$ where $X'[n] = g'(n)$ by the calculation,

\[ X' = \IFFT(C(\FFT(X))) \]
\[ C(F)[k,1] = \frac{-2 \pi (k-1)}{N} F[k,2] \]
\[ C(F)[k,2] = \frac{2 \pi (k-1)}{N} F[k,1] \]

\chapter{Future Subjects of Study}

The association between product spaces and null spaces. So, if we have $\shape{A} = \vec{a} \oplus \vec{n}$
then we'll define $ProdSpace(A, n)$ and $NullSpace(A, n)$ as the possible outputs of
\[ A \mmult{n} X = Y \]
And the possible solutions to,
\[ A \mmult{n} X = 0 \]
Respectively where in both cases $\shape{X} = \vec{n}$. 
Note that $ProdSpace(A, n) \subset R^{\vec{a}}$ and $NullSpace(A, n) \subset R^{\vec{n}}$

Now for any multimatrices $B$ and $C$ of the same shape, $\shape{B} = \shape{C} = \vec{s}$,
they are defined as 'orthogonal', i.e. $B \bot C$ iff $B \mmult{\shape{s}} C = 0$.
And two sets are orthogonal if all any member from one is orthogonal to any member of the other.

I hypothesize that,
\[ProdSpace(A, n) \bot NullSpace(\Tran(A, a), a)\]
and
\[NullSpace(A, n) \bot ProdSpace(\Tran(A, a), a)\]
based on a similar theory for 2d matrices \cite{youtube:orthogonal} (and the fact that the shapes line up nicely).

And from there I think you can derive a solution to the least squares problem for multimatrices.

If $B - A \mmult{n} X = E$ and where you want to minimize $SS(E)$, you could solve this with derivatives
but, notice that a shortest $E$ is necessarily orthogonal $ProdSpace(A,n)$ by simple geometry since it is a shortest
vector from $ProdSpace(A,n)$ to $B$. So if our above hypothesis is correct, $B$ is in $NullSpace(\Tran(A,a), a)$

Therefore the solution to $\Tran(A,a) \mmult{a} E = 0$ for $E$ will be the one that minimizes $SS(E)$. So,
\begin{align*}
  \Tran(A,a) \mmult{a} E &= 0 \\
  \Tran(A,a) \mmult{a} (B - A \mmult{n} X) &= 0 \\
  \Tran(A,a) \mmult{a} B - \Tran(A,a) \mmult{a} (A \mmult{n} X) &= 0 \\
  \Tran(A,a) \mmult{a} B - \Tran(A,a) \mmult{a} A \mmult{n} X &= 0 \\
  \Tran(A,a) \mmult{a} B &= \Tran(A,a) \mmult{a} A \mmult{n} X \\
  \Tran(A,a) \mmult{a} A \mmult{n} X &= \Tran(A,a) \mmult{a} B
\end{align*}

This brings to mind the fact that multimatrices themselves form a vector space. Basically, for any shape $\vec{x}$
there is an associated vector space of multimatrices $R^{\vec{x}}$. And I haven't yet explictly stated that. Need to do
that because I'm pretty sure that's necesary for the shortest path being the one that's orthoganal.

I think need to prove, in the abstract, that if you have a vector field $F$
and a distance metric $d(u,v)$ and a bilinear form \cite{wiki:bilinear}, $b(u,v)$, such that
\[ v \bot u \iff b(u,v) = 0 \]
Then for any $v \in F$ and any sub field $f \subset F$, for all $u \in f$,
\[ (v-u) \bot u \iff \forall u' \in f - \{u\} : d(u', v) < d(u,v) \]
That is, $u$ is the closest vector in $f$ to $v$ if and only if it is the orthoganal project of $v$ onto $f$.
